Ordinal Tax To Sustain a Digital Economy

### 2019-08-05 writing/short note on digital tax/DigitalTax.tex
minor adjustments in the writing.

\title{Idiosyncratic, Ordinal Tax To Sustain a Digital Economy}

@@

Recently, the French Senate approved a law that imposes a $3\%$ tax on revenue generated from digital services by companies above a certain size. 
While there is a lot of debate about political consequences of this action, it is actually interesting to reverse the question and instead ask what are the long-term implications of an economy with no such digital tax. 
More generally, we can see a digital service as a special case of products with low or zero cost of transportation. 
With basic economic models we show that an economy with no transportation costs is prone to monopolisation in that minuscule, random differences in quality are rewarded disproportionally. 
We then propose a distance-based tax to counter-balance the tendencies of random centralisation.  
Compared to an obvious tax that scales with physical (cardinal) distance, we show that a ranked (ordinal) distance tax leverages the benefits of digitalization while keeping the economy stable.

@@

>>>>

\title{Ordinal Tax To Sustain a Digital Economy}

@@

Recently, the French Senate approved a law that imposes a $3\%$ tax on revenue generated from digital services by companies above a certain size. 
While there is a lot of political debate about economic consequences of this action, it is actually interesting to reverse the question: 
We consider the long-term implications of an economy with no such digital tax. 
More generally, we can think of digital services as a special case of products with low or zero cost of transportation. 
With basic economic models we show that a market with no transportation costs is prone to monopolization as minuscule, random differences in quality are rewarded disproportionally. 
We then propose a distance-based tax to counter-balance the tendencies of random centralisation.  
Unlike a tax that scales with physical (cardinal) distance, a ranked (ordinal) distance tax leverages the benefits of digitalization while maintaining a stable economy.

@@

\section*{Acknowledgements} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

SC Lera acknowledges stimulating discussions with S. Donick.
